---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
---


# newAnno for ref.snSS2 Colon neurons               
           
##### load dependancies               
```{r message=FALSE, warning=FALSE, include=FALSE}
source("I:/Shared_win/projects/RNA_normal/analysis.10x.r")
```


after analysis of several public and local datasets of ENS neurons,          
here better to do re-clustering and new annotations for the first atlas data                 


## processed obj        

```{r}
ss2_neur.seur <- readRDS("./ss2_neur.seur_traj.rds")
ss2_neur.seur
```


```{r include=FALSE, paged.print=FALSE}
#head(ss2_neur.seur@meta.data)
ss2_neur.seur@meta.data[,c("Anno1","Anno2")] <- NULL
```


## re-clustering           


rerun current local method to match annotations of SI neurons      


```{r}
GEX.seur <- ss2_neur.seur
GEX.seur
```


### variable.new          

```{r message=FALSE, warning=FALSE,fig.width=12,fig.height=5}
GEX.seur <- FindVariableFeatures(GEX.seur, selection.method = "vst", nfeatures = 1500)

# Identify the 10 most highly variable genes
#top10 <- head(VariableFeatures(GEX.seur), 10)
top20 <- head(VariableFeatures(GEX.seur), 20)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(GEX.seur)
plot2 <- LabelPoints(plot = plot1, points = top20, repel = T)
plot1 + plot2
```


```{r}
head(VariableFeatures(GEX.seur), 200)
```

```{r}
GEX.seur <- ScaleData(GEX.seur, features = rownames(GEX.seur))
```

### PCA.new       

```{r}
# exclude MT genes  and more 
#
MT_gene <- grep("^mt-",rownames(GEX.seur),value = T)
GEX.seur[["percent.mt"]] <- PercentageFeatureSet(GEX.seur, features = MT_gene)
DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|Mzb1|Vpreb|Lars2|Jun|Fos|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AY|^AC|^AA|^AW|^BC|^Gm|^Hist|Rik$|-ps",
            rownames(GEX.seur),value = T)
CC_gene <- Hmisc::capitalize(tolower(as.vector(unlist(cc.genes.updated.2019))))


VariableFeatures(GEX.seur) <- setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,
                                                  DIG, 
                                                  CC_gene) )

GEX.seur <- RunPCA(GEX.seur, features = VariableFeatures(GEX.seur))
```


```{r}
length(setdiff(VariableFeatures(object = GEX.seur),
               c(MT_gene,DIG,CC_gene)))
setdiff(VariableFeatures(object = GEX.seur),
        c(MT_gene,DIG,CC_gene))[1:300]
```

```{r pca,fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "orig.ident") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "orig.ident")
```

```{r pcsheat,fig.width=12,fig.height=15}
DimHeatmap(GEX.seur, dims = 1:12, cells = 1500, balanced = TRUE,ncol = 4)
```


##### decide PCs to use          
     
```{r}
ElbowPlot(GEX.seur,ndims = 50)
```


```{r}
PCs <- 1:25
GEX.seur <- FindNeighbors(GEX.seur, dims = PCs, k.param = 20)
GEX.seur <- FindClusters(GEX.seur, method = 'igraph' ,resolution = 2)
```


### Run UMAP/tSNE    

```{r}
GEX.seur <- RunTSNE(GEX.seur, dims=PCs, complexity = 100)
GEX.seur <- RunUMAP(GEX.seur, dims=PCs, n.neighbors = 20, seed.use = 233)
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "tsne", label = T) + DimPlot(GEX.seur, reduction = "umap", label = T)
```


## new Annotations        


```{r}
# further remove low-quality/mix-like C24          
GEX.seur <- subset(GEX.seur, subset=seurat_clusters != 24)
GEX.seur
```

```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "tsne", label = T) + DimPlot(GEX.seur, reduction = "umap", label = T)
```

### sort_clusters       


```{r fig.width=12,fig.height=7.5}
FeaturePlot(GEX.seur, features = c(#"Chat"
                                   "Bnc2","Fut9","Nos1","Vip",
                                   "Gal","Moxd1","Sst","Calcb",
                                   "Nmu","Cdh9","Piezo2","Nxph2"),
            ncol = 4)
```


```{r}
GEX.seur$sort_clusters <- factor(as.character(GEX.seur$seurat_clusters),
                                 levels = c(0,1,16,12,6,18,13,         # Chat+Bnc2+ EMNs
                                            4,11,22,3,10,7,5,20,17,9,   # Nos1+ (Vip+) IMNs
                                            15,14,             # Gal+ IN1, Moxd1+ IN2
                                            2,               # Sst+ IN3
                                            21,23,           # Calcb+Nmu+ IPAN1, Cdh9+ IPAN2
                                            19,8            # Piezo2+ IPAN3, Nxph2+ IPAN4
                                            ))
```


#### check local final markers         


```{r}
markers.new.ss <- list(EMN=c("Chat","Bnc2","Tox","Ptprt",
                       "Gfra2","Oprk1","Adamtsl1", 
                       "Fbxw15","Fbxw24","Chrna7",
                       "Satb1","Itga6","Cntnap5b",
                       "Pgm5","Chgb",
                       "Nxph1",
                       "Gabrb1","Glp2r","Nebl",
                       "Lrrc7",
                       "Ryr3","Eda",
                       "Hgf","Lama2","Efnb2",
                       "Tac1",
                       "Kctd8",
                       "Ptn",
                       "Ntrk2","Penk","Itgb8",
                       "Fut9","Nfatc1","Egfr","Pdia5",
                       "Ahr","Mgll",
                       "Aff3",
                       "Chrm3"
                       ),
                 IMN=c("Nos1","Kcnab1",
                       "Gfra1","Etv1",
                       "Man1a","Airn",
                       "Adcy2",
                       "Col25a1",
                       "Cmah","Creb5","Vip","Pde1a",
                       "Ebf1","Gpc5","Mid1","Igfbp5",
                       "Ppara",
                       "Pcdh11x","Adcy8","Grp"
                       ),
                 IN=c("Npas3","Synpr","St18","Gal",
                      "Nova1",
                      "Cdh10","Kcnk13",
                      "Neurod6","Moxd1","Sctr",
                      "Piezo1","Vipr2","Adamts9","Sst","Kcnn2"
                      ),
                 IPAN=c("Calb2","Adcy1","Calcb","Nmu","Adgrg6","Pcdh10",
                        "Ngfr","Galr1","Il7","Aff2",
                        "Gpr149","Itgb6","Met","Itgbl1",
                        
                        "Cdh6","Cdh8",
                        "Clstn2","Ano2","Ntrk3",
                        "Cpne4","Vwc2l","Cdh9",
                        "Car10","Dcc",
                        "Scgn",
                        "Vcan","Cck","Piezo2","Kcnh7",
                        "Rerg","Bmpr1b","Skap1","Ntng1",
                        "Tafa2","Nxph2"))
```


```{r}
check.markers.ss <- as.vector(unlist(markers.new.ss))
check.markers.ss
```


```{r fig.height=5.5, fig.width=16.5}

pm.sort <- DotPlot(GEX.seur, features = check.markers.ss[check.markers.ss %in% rownames(GEX.seur)], group.by = "sort_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) 
pm.sort

```


### newAnno          


```{r}
# Anno1 is exactly as same as in Cell2020 fig.2a
GEX.seur$Anno1 <- GEX.seur$Annotation
```


```{r}
# Anno2 is modified in another version of ENC, ref to NatNeur2021 SI P21 data and a few local datasets 
GEX.seur$Anno2 <- as.character(GEX.seur$seurat_clusters)

GEX.seur$Anno2[GEX.seur$Anno2 %in% c(0,1,16)] <- "EMN1"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(12)] <- "EMN2"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(6)] <- "EMN3"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(18)] <- "EMN4"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(13)] <- "EMN5"

GEX.seur$Anno2[GEX.seur$Anno2 %in% c(4,11,22)] <- "IMN1"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(3,10,7,5)] <- "IMN2"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(17,20)] <- "IMN3"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(9)] <- "IMN4"

GEX.seur$Anno2[GEX.seur$Anno2 %in% c(15)] <- "IN1"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(14)] <- "IN2"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(2)] <- "IN3"

GEX.seur$Anno2[GEX.seur$Anno2 %in% c(21)] <- "IPAN1"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(23)] <- "IPAN2"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(19)] <- "IPAN3"
GEX.seur$Anno2[GEX.seur$Anno2 %in% c(8)] <- "IPAN4"

GEX.seur$Anno2 <- factor(GEX.seur$Anno2)

```




```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "Anno1", label.size = 2.45)  +
  DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "Anno2", label.size = 3.25)
``` 



```{r paged.print=FALSE}
head(GEX.seur@meta.data)
```


```{r fig.width=12.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "Anno1", label.size = 2.35)  +
  DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "Anno2", label.size = 3.5)
```  


```{r fig.height=5.5, fig.width=16.5}

pm.A2 <- DotPlot(GEX.seur, features = check.markers.ss[check.markers.ss %in% rownames(GEX.seur)], group.by = "Anno2",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) 
pm.A2

```


```{r}
#saveRDS(GEX.seur,"ss2_neur.newAnno2024.rds")
```












